Arc Blanc: a real time ocean simulation framework

### 2025-01-10 paper.tex
Fixed sign typos in appendix A
Reordered appendix A for velocity calculation to improve coherency

	\tilde{\phi}(y, t,\mathbf{k})=\frac{ig}{\omega(k)} E(\mathbf{k},y) \left(\tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)+\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t)\right)

@@

	                      & \times \frac{ig}{\omega(k)}\left(\tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)+\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t)\right)

@@

	                      & \times \frac{ig}{\omega(k)}\left(\tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)+\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t)\right) \exp\left(i \mathbf{k}\cdot \mathbf{x}\right)

@@

	\frac{\partial E(\mathbf{k},y)}{\partial y}\frac{ig}{\omega(k)}\left(\tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)+\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t)\right)\exp\left(i\mathbf{k}\cdot\mathbf x\right)               \\

@@

	                                                 & \times\frac{ig}{\omega(k)}\left(\tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)+\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t)\right)\exp\left(i\mathbf{k}\cdot\mathbf x\right)

@@

This expression is valid for height $y\leq0$, but not usable above for $y>0$.
Several possibilities exist to overcome this problem:
\begin{enumerate}
	\item The most naive one assumes $E(\mathbf k,y>0)=1$.
	\item A more realistic solution is based on a linear extrapolation using the derivative at $y=0$, as follows:
	      \begin{equation}
		      \label{equa:attenuationExtrapolation}
		      E(\mathbf{k}, y)=
		      \begin{cases}
			      E(\mathbf k,0)+y\frac{\partial E}{\partial y}(\mathbf k,0) & \text{if~}y>0, \\
			      \exp(ky)                                                   & \text{else.}
		      \end{cases}
	      \end{equation}
\end{enumerate}

@@

Equation~\ref{equa:attenuationDeep1} and the definition of potential velocity $\nabla\phi=\mathbf{v}$ lead to the velocity $\mathbf{v}$. First, function $\tilde{\phi}$ is rewritten as follows:
\begin{equation}
	\tilde{\phi}(y,t,\mathbf{k})=\frac{ig}{\omega(k)} E(\mathbf{k},y) \left(\tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)+\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t)\right).
\end{equation}
Then the gradient of $\phi$ is as follows:
\begin{equation}
	\nabla \phi = \begin{pmatrix}
		v_x \\
		v_y \\
		v_z
	\end{pmatrix} =\tilde{\mathbf{v}}(y,\mathbf{k},t)\exp\left(i\mathbf{k}\cdot\mathbf{x}\right)
\end{equation}
where $\tilde{\mathbf{v}}(\mathbf{k},t,y)$ is the vector equal to:
\begin{equation}
	\tilde{\mathbf{v}}(y,\mathbf{k},t) = \exp(ky)\left(\tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)-\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t)\right)
	\begin{pmatrix}
		\frac{-k_xg}{\omega(k)} \\
		i\omega(k)              \\
		\frac{-k_zg}{\omega(k)}
	\end{pmatrix}.
\end{equation}
Finally, reintroducing a sum on a set of waves vectors $\mathbf{k}$ leads to:
\begin{equation}
	\nabla \phi =
	\sum_{\mathbf{k}}\tilde{\mathbf{v}}(\mathbf{k},t, y)\exp\left(i\mathbf{k}\cdot\mathbf{x}\right)
\end{equation}

>>>>

	\tilde{\phi}(y, t,\mathbf{k})=\frac{ig}{\omega(k)} E(\mathbf{k},y) \left(\tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)-\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t)\right)

@@

	                      & \times \frac{ig}{\omega(k)}\left(\tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)-\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t)\right)

@@

	                      & \times \frac{ig}{\omega(k)}\left(\tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)-\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t)\right) \exp\left(i \mathbf{k}\cdot \mathbf{x}\right)

@@

	\frac{\partial E(\mathbf{k},y)}{\partial y}\frac{ig}{\omega(k)}\left(\tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)-\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t)\right)\exp\left(i\mathbf{k}\cdot\mathbf x\right)               \\

@@

	                                                 & \times\frac{ig}{\omega(k)}\left(\tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)-\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t)\right)\exp\left(i\mathbf{k}\cdot\mathbf x\right)

@@

Equation~\ref{equa:attenuationDeep1} and the definition of potential velocity $\nabla\phi=\mathbf{v}$ lead to the velocity $\mathbf{v}$. First, function $\tilde{\phi}$ is rewritten as follows:
\begin{equation}
	\tilde{\phi}(y,t,\mathbf{k})=\frac{ig}{\omega(k)} E(\mathbf{k},y) \left(\tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)-\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t)\right).
\end{equation}
Then the gradient of $\phi$ is as follows:
\begin{equation}
	\nabla \phi = \begin{pmatrix}
		v_x \\
		v_y \\
		v_z
	\end{pmatrix} =\tilde{\mathbf{v}}(y,\mathbf{k},t)\exp\left(i\mathbf{k}\cdot\mathbf{x}\right)
\end{equation}
where $\tilde{\mathbf{v}}(\mathbf{k},t,y)$ is the vector equal to:
\begin{equation}
	\tilde{\mathbf{v}}\left(\mathbf{k},t,y\right)=%
	E\left(\mathbf{k},y\right)\left(\tilde{h}_0\left(\mathbf{k}\right)\exp\left({i\omega(k)t}\right)-\tilde{h}_0^*\left(-\mathbf{k}\right)\exp\left({-i\omega(k)t}\right)\right)
	\left[
		\begin{array}{c}
			\displaystyle\frac{-k_xg}{\omega(k)} \\
			\displaystyle i\omega(k)             \\
			\displaystyle\frac{-k_zg}{\omega(k)}
		\end{array}
		\right],
\end{equation}

Finally, reintroducing a sum on a set of waves vectors $\mathbf{k}$ leads to:
\begin{equation}
	\nabla \phi =
	\sum_{\mathbf{k}}\tilde{\mathbf{v}}(\mathbf{k},t, y)\exp\left(i\mathbf{k}\cdot\mathbf{x}\right).
\end{equation}

Note that the expression of $E\left(\mathbf{k},y\right)$ (see Equation \ref{equa:attenuationDeep1}) is valid for height $y\leq0$, but not usable above for $y>0$.
Several possibilities exist to overcome this problem:
\begin{enumerate}
	\item The most naive one assumes $E(\mathbf k,y>0)=1$.
	\item A more realistic solution is based on a linear extrapolation using the derivative at $y=0$, as follows:
	      \begin{equation}
		      \label{equa:attenuationExtrapolation}
		      E(\mathbf{k}, y)=
		      \begin{cases}
			      E(\mathbf k,0)+y\frac{\partial E}{\partial y}(\mathbf k,0) & \text{if~}y>0, \\
			      \exp(ky)                                                   & \text{else.}
		      \end{cases}
	      \end{equation}
\end{enumerate}

@@
